---
title: "Drive change with big data"
author: Professor Rob J Hyndman
date: ""
classoption: compress,aspectratio=169
toc: false
output:
  binb::monash:
    keep_tex: yes
    includes:
      in_header: preamble.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, cache=TRUE, dev.args=list(bg=grey(0.9), pointsize=11))
```

```{r loadpackages}
library(gridExtra)
library(ggplot2)
library(knitr)
library(tidyverse)
library(viridis)
library(lubridate)
library(tsibble)
library(ggwordcloud)
library(maps)
library(gapminder)
library(gganimate)
```


## Data is collected everywhere and at any time

\begin{textblock}{7.8}(1,1.4)
\begin{block}{}
The ability to make data-driven decisions is crucial to any organization.
\end{block}
\end{textblock}

\vspace*{1.8cm}

```{r animation, cache = TRUE, fig.width=6, fig.height=4,fig.show='animate', interval=1/5,aniopts='loop,width=8.2cm'}
#Modified from
#https://gist.github.com/thomasp85/05169ad44ddcc8ed56da6ff7bf7fbe36

anim <- gapminder %>%
  ggplot(aes(x = gdpPercap, y=lifeExp, size = 3*pop, colour = country)) +
  geom_point(show.legend = FALSE, alpha = 0.9) +
  scale_color_viridis_d(option ="magma") +
  scale_size(range = c(5, 20)) +
  scale_x_log10() +
  labs(title = 'Year: {frame_time}', x = 'GDP per capita', y = 'Life expectancy') +
  transition_time(year) +
  shadow_wake(wake_length = 0.15, size = 0.9,  alpha = FALSE)
anim
anim_save(filename ="figs/animation.png", animation=anim, device='png')
```

<!-- \begin{textblock}{18}(.3,3.2) -->
<!-- \animategraphics[autoplay,loop,height=2.3in]{5}{./figs/animation}{1}{100} -->
<!-- \end{textblock} -->

\placefig{10}{1.35}{height=7.8cm, width=6.0cm}{data-never-sleeps}

\begin{textblock}{6}(10.2,8.7)
 \fontsize{7}{8}\sf\texttt{www.domo.com/learn/data-never-sleeps-7}
\end{textblock}

## A 10 year forecast

\placefig{0}{1.35}{height=8.2cm}{hal-varian}

\begin{textblock}{5.55}(10.3,1.1)\fontsize{13.5}{14}\sf
\begin{alertblock}{Hal Varian, Chief~Economist, Google:}
I keep saying the sexy job in the next ten years will be statisticians. People think I’m joking, but \dots\ the ability to take data---to be able to understand it, to process it, to extract value from it, to visualize it, to communicate it---that’s going to be a hugely important skill in the next decades.\hfill{\itshape (2009)}
\end{alertblock}
\end{textblock}

## Best jobs in the world (2019)

1. **Data Scientist** (19\% growth)
2. **Statistician** (33\% growth)
3. University Professor
4. Occupational Therapist
5. Genetic Counselor
6. Medical Services Manager
7. Information Security Analyst
8. Mathematician
9. Operations Research Analyst
10. Actuary

\only<2>{\begin{textblock}{6.3}(8.5,.3)\fontsize{13}{14}\sf
\begin{block}{}
\begin{itemize}
\item Median salary US\$114K
\item Strong sustained projected growth
\item Good working environment, low stress, interesting problems
\end{itemize}
\end{block}
\end{textblock}}

\begin{textblock}{10}(5.4,8.4)
\fontsize{9}{10}\sf\texttt{https://www.careercast.com/jobs-rated/best-jobs-of-2019}
\end{textblock}

\vspace*{4cm}

## Why Business Analytics?
\fontsize{15}{17}\sf

**Organizations need to make:**

\begin{itemize}
 \item[\faPaperPlaneO] Informed decisions based on facts  \faAreaChart \pause
 \item[\faPaperPlaneO] Facts are measured with data \faDownload \pause
 \item[\faPaperPlaneO] Business analytics experts use statistical and computational
methods to answer business relevant questions using data \faCogs \pause
 \item[\faPaperPlaneO] Business analytic professionals are able to communicate findings
to experts and broad audiences \faComments
\end{itemize}

## Master of Business Analytics \textrightarrow\ Starting 2020

\begin{textblock}{5.9}(0.4,1.35)
 \fontsize{13.2}{14.5}\sf
   \begin{block}{}
    \begin{itemize}\itemsep=7pt
     \item[\faArrowRight]  Learn end-to-end analytics including data collection,
     modeling, collaboration \& communication
     \item[\faArrowRight]  Broad foundation: statistical thinking, probabilistic
     modeling \& computational techniques
     \item[\faArrowRight]  Social conscience, working for a better world
    \end{itemize}
   \end{block}
\end{textblock}


\placefig{6.2}{1.4}{width=10cm}{starwars-rey-rstats.png}

\begin{textblock}{8}(13.2,8.7)\fontsize{7}{7}\sf
Artwork by @allison\_horst
\end{textblock}

## &nbsp;

\placefig{.5}{.2}{height=4.5cm}{RStudio-Ball}

\begin{textblock}{8.5}(6.5,.5)\fontsize{13}{14}\sf
\begin{block}{}
\begin{itemize}\tightlist
\item The leading statistical programming framework.
\item Completely free and open-source
\item Used by every major company in the world
\item Supported by Microsoft, Google, Facebook, Amazon, etc
\end{itemize}
\end{block}
\begin{block}{}
\begin{itemize}\tightlist
\item Monash instructors have written many widely used R packages
\item Monash instructors are engaged with the international R community.
\item Leading R developers visit Monash regularly.
\end{itemize}
\end{block}
\end{textblock}

\begin{textblock}{4.9}(.5,4.7)
\begin{alertblock}{}
Monash MBAT is the only masters course in the world based entirely around R and taught by leading R developers.
\end{alertblock}
\end{textblock}

## Master of Business Analytics \textrightarrow\ Starting 2020

\begin{textblock}{7}(8.6,1.35)
\fontsize{14}{16}\sf
\begin{alertblock}{}
\begin{itemize}\tightlist
\item Taught by internationally renowned researchers.
\item Cutting edge, focusing on problem solving and hands-on experience.
\item Focus on wild data, real problems. We regularly advise industry and government.
\item Fiercely independent: we only teach open-source software.
\end{itemize}
\end{alertblock}
\end{textblock}

\placefig{.2}{1.4}{width=8.25cm}{welcome_to_rstats_twitter.png}

\begin{textblock}{8}(0.2,8.7)\fontsize{7}{7}\sf
Artwork by @allison\_horst
\end{textblock}


## MBAT users profile
\fontsize{15}{17}\sf

\begin{itemize}
 \item[\faChevronRight] At least \textbf{\color{blue1}{one unit of undergraduate statistics}}.\pause
 \item[\faChevronRight] An \textbf{\color{blue1}{interest}} in using \textbf{\color{blue1}{data}}
  to solve problems and uncover truths.\pause
 \item[\faChevronRight] A combination of \textbf{\color{blue1}{ curiosity in quantitative  and computational
  methods}} with a \textbf{\color{blue1}{desire}} to make a difference.\pause
 \item[\faChevronRight] An \textbf{\color{blue1}{undergraduate degree}} that has sparked your interest to work
 with data to answer real life questions.
\end{itemize}

## \faUniversity\quad MBAT Units

\begin{block}{A: Advanced preparatory studies (24 credit points)}
 \begin{itemize}
  \item  ETC5510: Introduction to data analysis
  \item  ETC5242: Statistical thinking
  \item  ETC5250: Introduction to machine learning
  \item  ETC5550: Applied forecasting
 \end{itemize}
\end{block}
\faArrowRight \hphantom{} Depending on prior qualifications, credits might be received for (A)

\faArrowRight \hphantom{} All students will complete (B) and (C)

## \faUniversity\quad MBAT Units

\begin{block}{B: Mastery knowledge (48 credit points)}
 \begin{itemize}\itemsep=2pt
  \item  ETC5512: Wild-caught data
  \item  ETC5513: Collaborative and reproducible practices
  \item  ETC5521: Exploratory data analysis
  \item  ETC5523: Communicating with data
  \item  ETF5500: High dimensional data analysis
  \item  ETC5555: Statistical machine learning
  \item  ETC5580: Advanced statistical modelling
  \item  ETC5543: Business analytics creative activity\\
  (12 points internship or research project)
 \end{itemize}
\end{block}

## \faUniversity\quad MBAT Units

\begin{block}{C: Application studies (24 credit points)}
\textbf{Four elective units}
 \begin{itemize}\itemsep=2pt
  \item FIT9133 Programming foundations in Python
  \item FIT5205 Data in society
  \item FIT9132 Introduction to databases
  \item MAT9004 Mathematical foundations for data science
  \item ETC5410 Bayesian time series econometrics
  \item FIT5147 Data exploration and visualisation
  \item ETC5555 Statistical machine learning
  \item FIT5212 Data analysis for semi-structured data
 \end{itemize}
\end{block}


## \faGraduationCap\quad MBAT: A World full of opportunities

\begin{block}{}
  \begin{itemize}
  \item \textbf{\color{blue1}{Location and duration:}} 1.5 or 2 years full time
          or 3 or 4 years part time @ Monash Clayton.
   \item \textbf{\color{blue1}{Applications}} for our Semester 1 intake (February 2020) are now open (including a candidate statement).
   \item \textbf{\color{blue1}{Entry requirements:}} Australian bachelor's degree or an equivalent qualification
    with a weighted average mark (WAM) of 65, or equivalent
    GPA as determined by the School.
  \end{itemize}
\end{block}



##

\placefig{-0.01}{-0.01}{width=1.01\paperwidth,height=\paperheight}{ana-bg-2-rect}

\begin{textblock}{12}(.4,.2)
 \color{white}{\fontsize{17}{17}\texttt{monash.edu/business/master-of-business-analytics}}
\end{textblock}

\begin{textblock}{7.5}(.5,4.5)\fontsize{28}{30}\sf\bfseries\color{white}\raggedright\par
  Many thanks!\\[1cm]
  Questions?
\end{textblock}





